\bf What is the Best Way to Display Two Time Series to Read Association?

### 2016-02-04 paper/paper.Rnw
equation
grammar

Temporal dependence is present in many macroeconomic variables \citep{Nelson, Perron} and in financial data \citep{Sher, Turtle}. It is a common, but untested, belief that the inclusion of time in the graphics will increase the detail of information displayed and allow relationships to be examined more comprehensively, so many analysts utilise the overlaid line graph to examine their data (Figure \ref{nzd}). In the field of statistics, the recommendation for exploring association visually is to use a scatterplot. There is substantial literature supporting this \citep{Cleveland, Harrison, Li}.  However, it is still common that when the two variables are temporal they are displayed as overlaid time series (line graphs). In this paper we have utilized new methods for rigorously comparing plot design, using visual inference, to investigate which is the best display if reading association is important.

@@

\begin{eqnarray} 
\label{modelpower}
Power_{ijklt} &=& \psi \{ \beta_{0} + \beta_{1} x_{1,i}  + \beta_{2} x_{2,j}  + \beta_{3} x_{3,k} + \beta_{4} x_{4,t} + \\
 & & \beta_{5} x_{1,i} \* x_{2,j} + \beta_{6} x_{5,l}(\beta_{7} + \beta_{8} x_{1,i}  + \beta_{9} x_{2,j}  + \beta_{10} x_{3,k} + \nonumber \\
 & & \beta_{11} x_{4,t} + \beta_{12} x_{1,i} \* x_{2,j}) + \gamma z_{s} + \epsilon_{ijklt} \} \nonumber
\end{eqnarray}

@@

\begin{eqnarray} 
\label{timemodel}
ln(time_{ijklmt}) &=& \beta_{0} + \beta_{1} x_{1,i}  + \beta_{2} x_{2,j}  + \beta_{3} x_{3,k} + \beta_{4} x_{4,t} + \\
 & & \beta_{5} x_{1,i} \* x_{2,j} + \beta_{6} x_{5,l}\*(\beta_{7} + \beta_{8} x_{1,i}  + \beta_{9} x_{2,j}  + \beta_{10} x_{3,k} + \nonumber\\
 & & \beta_{11} x_{4,t} + \beta_{12} x_{1,i} \* x_{2,j}) + \gamma z_{s} + \epsilon_{ijklt} \nonumber 
\end{eqnarray}

Other than the removal of the link functon, the structure of the model identical to that in Equation~\ref{modelpower}.

>>>>

Temporal dependence is present in many macroeconomic variables \citep{Nelson, Perron} and in financial data \citep{Sher, Turtle}. It is a common, but untested, belief that the inclusion of time in the graphics will increase the detail of information displayed and allow relationships to be examined more comprehensively, so many analysts utilise the overlaid line graph to examine their data (Figure \ref{nzd}). In the field of statistics, the recommendation for exploring association visually is to use a scatterplot. There is substantial literature supporting this \citep{Cleveland, Harrison, Li}.  However, it is still common that when the two variables are temporal they are displayed as an overlaid time series (line graphs). In this paper we have utilized new methods for rigorously comparing plot design, using visual inference, to investigate which is the best display if reading association is important.

@@

\begin{eqnarray} 
\label{modelpower}
Power_{ijklt} &=& \psi \{ \beta_{0} + \beta_{1} x_{1,i}  + \beta_{2} x_{2,j}  + \beta_{3} x_{1,i} \* x_{2,j} + \beta_{4} x_{3,k} + \nonumber \\
 & & \beta_{5} x_{4,t} + x_{5,l}(\beta_{6} + \beta_{7} x_{1,i}  + \beta_{8} x_{2,j}  + \nonumber \\
 & & \beta_{9} x_{1,i} \* x_{2,j} + \beta_{10} x_{3,k} + \beta_{11} x_{4,t})  + \gamma z_{s} + \epsilon_{ijklt} \} \nonumber
\end{eqnarray}

@@

\begin{eqnarray} 
\label{timemodel}
ln(time_{ijklt}) &=& \{ \beta_{0} + \beta_{1} x_{1,i}  + \beta_{2} x_{2,j}  + \beta_{3} x_{1,i} \* x_{2,j} + \beta_{4} x_{3,k} + \nonumber \\
 & & \beta_{5} x_{4,t} + x_{5,l}(\beta_{6} + \beta_{7} x_{1,i}  + \beta_{8} x_{2,j}  + \nonumber \\
 & & \beta_{9} x_{1,i} \* x_{2,j} + \beta_{10} x_{3,k} + \beta_{11} x_{4,t})  + \gamma z_{s} + \epsilon_{ijklt} \} \nonumber 
\end{eqnarray}

Other than the removal of the link function, the structure of the model identical to that in Equation~\ref{modelpower}.
